---
title: "CLT_WUP"
author: "Jarrod Harris "
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
```
```{r}
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p
```

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
 
```{r}           
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))
```

```{r}
numb = 9
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg


p <- ggplot(my1000, aes(x=k9),Col=sex) + 
  geom_density() +

  # Add mean line
 geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
```

```{r}
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")
```

```{r}           
print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))
```

The mean will always get close to 50 and the standard deviation is getting smaller. This makes sense since the dividing number in the standard deviation formula is getting bigger, when we predict using 41.38 as the sample standard deviation and use sqrt(9) as the sample size we see the predicted value to be 13.79333 and this is pretty close to the approximate value of 14 for the standard deviation.

```{r}
numb=16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg

p <- ggplot(my1000, aes(x=k16), (Col=sex))+
geom_density()

p + ggtitle("n = 16") +
xlab("temperature") + ylab("density")
```

```{r}
print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))
```

The mean will always get close to 50 but always around 49. The standard deviation is smaller being around 11 compared to the approximate value of n=9’s 14 standard deviation. Predicting the standard deviation value using sqrt(16) we get about 10.345 being relatively close to the approximate value of 11.

```{r}
numb=25
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg

p <- ggplot(my1000, aes(x=k25), (Col=sex))+
geom_density()

p + ggtitle("n = 25") +
xlab("temperature") + ylab("density")
```

```{r}
print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))
```

The mean is still close to 50 and the standard deviation has decreased to be approximately 8. A predicted standard deviation using sqrt(25) gives us about 8.276 which is still close for the approximate value of 8. The graph is starting to look more similar on the sides but the tip at around 50 does stand out more often with different data.

```{r}
numb=36
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg

p <- ggplot(my1000, aes(x=k36), (Col=sex))+
geom_density()

p + ggtitle("n = 36") +
xlab("temperature") + ylab("density")
```

```{r}
print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))
```

The mean is still close to 50 and the standard deviation has decreased to be approximately 7. If we use sqrt (36) to predict the standard deviation we get about 6.89667. The graphs sides now look smooth not seeing the bumps unlike using smaller sample sizes.
